### 2016-01-18 papers/CAFe/HIPS-paper/conclusions.tex
final changes
Fixed a few typos.

An intriguing \emph{possibility} exists for automatic conversion of CAFe codes to OCR exists:
\begin{itemize}
\item
  CAF codes have well defined boundaries (called segment boundaries) indicating where new
  OCR tasks must be created.
\item
  CAF has many fewer library routines (primarily collectives) that must be converted.
\item
  CAF has events that already define some of the dependencies necessary for the creation
  of OCR tasks.
\item
  CAFe introduces the notion of task based parallelism (in addition to the existing
  Fortran constructs like \texttt{do concurrent}.
\end{itemize}

In the future we hope to examine \emph{if} the possibility exists for CAFe codes to be
automatically converted to an entirely differently programming paradigm like
the Open Community Runtime.

>>>>

An intriguing \emph{possibility} exists for automatic conversion of CAFe codes to OCR:
\begin{itemize}
\item
  CAF codes have well defined boundaries (called segment boundaries) indicating where new
  OCR tasks must be created.
\item
  CAF has many fewer library routines (primarily collectives) that must be converted.
\item
  CAF has events that already define some of the dependencies necessary for the creation
  of OCR tasks.
\item
  CAFe introduces the notion of task based parallelism (in addition to the existing
  Fortran constructs like \texttt{do concurrent}).
\end{itemize}

In the future we hope to examine \emph{if} the possibility exists for CAFe codes to be
automatically converted to an entirely different programming paradigm like
the Open Community Runtime.  Given the change in architectures being considered for
future HPC platforms it is likely that similar, novel runtime models will be proposed,
and we believe that CAFe provides a viable programming model for compiler-based mapping to
these new systems.
